\thetitle

### 2021-05-14 writing/discussion.tex
fix language, add explanation of mistake in take5

Interpreting the numeric summaries and aggregations of the last section demands an intuitive understanding of what blame trails look like in practice.
Thus, before drawing high level conclusions, let us examine one set of trails from a typical debugging scenario from the {\tt take5} benchmark,
whose module dependency graph is shown in the top left of figure~\ref{fig:example-trails}.

The rest of figure~\ref{fig:example-trails} illustrates the blame trails produced by every mode of the rational programmer (except Random) for the debugging scenario in
two different ways: 
\begin{itemize}

@@

In illustration of how to read the table, let us contrast rows 1 and~4. The first one shows that running the root
configuration under the Natural-blame mode fails due a dynamic type check and
blames the {\tt player} module; typing that module and running again then
results in a type error, and hence the trail is successful.  By contrast, the
Natural-exceptions mode (row 4) yields stack information for the root
configuration that is unhelpful; it identifies only {\tt main}, which is already
typed. Hence, this trail immediately gets stuck.

>>>>

Interpreting the numeric summaries and aggregations of the last section demands
an intuitive understanding of what blame trails look like in practice.  A
concrete example of blame trails and programmer modes is a good basis for
synthesizing this kind of intuition.

Figure~\ref{fig:example-trails} summarizes one particularly interesting
debugging scenario from the {\tt take5} benchmark. The module dependency graph
of this benchmark is shown in the top left of the figure. Its mutated {\tt
player} module provides a method under a different name than the client module,
{\tt dealer}, expects. In Typed Racket's gradual type system, this mistake
corresponds to a type-impedance mismatch---and all rational-programmer modes
come to different conclusions.

The rest of figure~\ref{fig:example-trails} illustrates the blame trails for
every mode of the rational programmer (except Random) for the debugging scenario
in two different ways:
\begin{itemize}

@@

To make this table concrete, compare rows 1 and~4. The first one shows that
running the root configuration under the Natural-blame mode fails due a dynamic
type check and blames the {\tt player} module; typing that module and running
again then results in a type error, and hence the trail is successful.  By
contrast, the Natural-exceptions mode (row 4) yields stack information for the
root configuration that is unhelpful; it identifies only {\tt main}, which is
already typed. Hence, this trail immediately gets stuck.
